---
title: "FYE-bioinfo"
output: html_document
---
Start by reading the data file
```{r}
covid.data <- read.csv("covid19_variants.csv")
covid.data
```
loading the lubridate package so I can organize the dates

```{r}
library(lubridate)
```


Assigning a new colum where the date is in the year, month, day format. I think it looks like the data came with this format in the date column, but I am doing this just to be safe.
```{r}
covid.data$as_of_date <- ymd(covid.data$date)
```
loading the dplyr package
```{r}
install.packages("dplyr")
library(dplyr)
```
just checking the dataframe to make sure that everything looks right and my column was added
```{r}
covid.data

```
```{r}
install.packages("ggplot2")
```
realizing I hadn't installed ggplot and adding that package, then I am just checking to see what the graph looks like before I make any changes.
```{r}
library(ggplot2)
ggplot(covid.data, aes(x=as_of_date, y=percentage, group=variant_name, color=variant_name))+
  geom_line()
```
I want to remove total and other from the plot so that I am just looking at the variants that we are interested in. (I am sure that there is a better, more concise way of writing this code, but this is all I got)
```{r}
#removing Total and other from the dataset
covid.data.nototal <-filter(covid.data, variant_name !="Total")
covid.data.nototal
```

```{r}
#removing other from the dataset
covid.data.variantonly <-filter(covid.data.nototal, variant_name !="Other")
covid.data.variantonly
```
Now I am plotting it again this time without the total and other variables.

```{r}

ggplot(covid.data.variantonly, aes(x=as_of_date, y=percentage, group=variant_name, color=variant_name))+
  geom_line()
```
Now I am assigning my graph to a variable just so it is a little less busy, while I add formating for the date 
```{r}
p<-ggplot(covid.data.variantonly) +
  aes(as_of_date,
      percentage, 
      group=variant_name, color=variant_name) +
  geom_line() +
  labs(x="Date", y="Percentage of sequenced specimens",
       title="Covid19 Variants in California")
      
```

The graph looks how I want it to now
```{r}
p+scale_x_date(date_labels = "%b %Y")
```
Uploading to Github

```{r}
install.packages("usethis")
library(usethis)
create_github_token()
```

```{r}
install.packages("gitcreds")
library(gitcreds)
gitcreds_set()
```

